\mytitle

### 2016-11-06 pdocs/thesis/article-section-3.tex
article polishing

Method btSequentialImpulseConstraintSolver::solveGroupCacheFriendlySetup
in \cbullet\ is used to get values for the internal variables described in Figure \ref{fig:solVars}.

@@

\begin {table}
\tbl {Simulation values for the unconstrained case with continuous collision detection.}{ 
\begin{tabular}{|l| l|l| l|l|l|l|l|}
\hline
{\bf Time} & 
{\bf Location} &
{\it velError} & {\it pene-} & {\it rhs} &
{\bf Velocity} & 
{\bf Impulse} \\ 
 &  & & {\it tration} &  &
 &  \\ 
 \hline
0.017 &  -0.003 & & &  &-0.17 & 0 \\  \hline
0.550 &  -1.500 & 3.5 & 0.033 & 21000& -2 & 21000 \\  \hline
0.567 &  -1.500 & 2.17 & 0 &  8100 & 0.01 & 13000 \\  \hline
0.583 &  -1.500 & 0.15 & 0 & 600  & 0 & 937 \\  \hline
0.600 &  -1.500 & 0.17 & 0 & 600  & 0 & 1040 \\  \hline
\end {tabular}}
\end {table}

>>>>

Method \mbox{btSequentialImpulseConstraintSolver::} \mbox{solveGroupCacheFriendlySetup}
in \cbullet\ is used to get values for the internal variables described in Figure \ref{fig:solVars}.

@@

\begin {table}
\tbl {Simulation values for the unconstrained case with continuous collision detection.}{ 
\begin{tabular}{|l| l|l| l|l|l|l|l|}
\hline
{\bf Time} & 
{\bf Location} &
{\it velError} & {\it pene-} & {\it rhs} &
{\bf Velocity} & 
{\bf Impulse} \\ 
 &  & & {\it tration} &  &
 &  \\ 
 \hline
0.017 &  -0.003 & & &  &-0.17 & 0 \\  \hline
0.550 &  -1.500 & 3.5 & 0.033 & 21000& -2 & 21000 \\  \hline
0.567 &  -1.500 & 2.17 & 0 &  8100 & 0.01 & 13000 \\  \hline
0.583 &  -1.500 & 0.15 & 0 & 600  & 0 & 937 \\  \hline
0.600 &  -1.500 & 0.17 & 0 & 600  & 0 & 1040 \\  \hline
\end {tabular}}
\label{tab:freeBlockValuesWithCcd} 
\end {table}
